---
title: "Development actions history"
output: html_document
editor_options: 
  chunk_output_type: console
---

All commands that you use to use when developing packages...

# First time just after creating the project

- Fill the following chunk to create the DESCRIPTION of your package

```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "leafler.polygonstyler",
    Description = "change color of polygon without reload geometries.",
    `Authors@R` = c(
      person("Lucas", "Longour", email = "lucas.longour@ird.fr", role = c("aut", "cre"))
    )
  )
)
# Define License with use_*_license()
usethis::use_mit_license("Lucas Longour")
```

# Start using git

```{r, eval=FALSE}
# usethis::use_git()
# # Deal with classical files to ignore
# usethis::git_vaccinate()
# # Use main for primary branch
# usethis::git_default_branch_rename()
```

# Set extra sources of documentation

```{r, eval=FALSE}
# Install a first time
# remotes::install_local()
# README
usethis::use_readme_rmd()
# Code of Conduct
# usethis::use_code_of_conduct("contact@fake.com")
# NEWS
# usethis::use_news_md()
```

**From now, you will need to "inflate" your package at least once to be able to use the following commands. Let's go to your flat template, and come back here later if/when needed.**


# Package development tools
## Use once

```{r, eval=FALSE}
# Pipe
# usethis::use_pipe()

# package-level documentation
usethis::use_package_doc()

# _GitLab
# gitlabr::use_gitlab_ci(type = "check-coverage-pkgdown")

# Add new flat template
# fusen::add_flat_template("add")
```

## Use everytime needed

```{r}
# Simulate package installation
pkgload::load_all()

# Generate documentation and deal with dependencies
attachment::att_amend_desc()

# Check the package
devtools::check()
```

# Share the package

```{r}
# set and try pkgdown documentation website
usethis::use_pkgdown()
pkgdown::build_site()

# build the tar.gz with vignettes to share with others
devtools::build()
```

